RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-15 paper/two_pager.tex
Add robustness section back in

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{subfigure}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\graphicspath{ {images/} }
\title{RBE/CS549 Project: Boat Tracking/Detection}
\author{Jordan Burklund \and James Kuszmaul}
\begin{document}
\maketitle

@@

Overall, the object pipeline is as follows:
\begin{figure}[H]
\includegraphics[width=16cm]{algorithm_flowchart}
\centering
\caption{High-Level Image Processing Pipeline}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=7.8cm]{hsv_kmeans2_orig}
\includegraphics[width=8.5cm]{hsv_kmeans2_suppressed}
\centering
\caption{Boat Confidence Results}
\label{fig:boatconf}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diff_magnitude}
\caption{Difference between the measured and modelled optical flow.
         Dark blue means perfect match, bright yellow means a poor match (and
         higher likelihood of an object).
         The sky is later filtered out by ignoring that half of the image.}
\label{fig:diff_magnitude}
\end{figure}

\begin{figure}
\hfill
\subfigure[Blobs pre-filtering]{\includegraphics[width=0.3\textwidth]{threshold_bwlabel}}
\hfill
\subfigure[Blobs
post-filtering]{\includegraphics[width=0.3\textwidth]{filtered_labels}}
\hfill
\caption{Results of blob detection on HSV and optical flow confidences}
\label{fig:blobs}
\end{figure}

@@

\begin{description}
\item[\url{https://drive.google.com/file/d/1FoKWkp5xDSKwp5YyluKrclo_kGFU4gsg/view?usp=sharing}]
  In this video we have a longer view of the same boat as Figure
  \ref{fig:example_detection}
\item[\url{https://drive.google.com/file/d/1ndVSwF77_4va6U8rWT4FGJOXq1AjKL_Z/view?usp=sharing}]
  This has a slightly shorter capture of a different boat, indicating some
  degree of robustness to different individual instances
  \ref{fig:example_detection}
\end{description}

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{subfigure}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\graphicspath{ {images/} }

\begin{document}

\title{RBE/CS549 Project: Boat Tracking/Detection}
\author{\IEEEauthorblockN{Jordan Burklund \and James Kuszmaul}}
\maketitle

@@

Overall, the object pipeline is as follows:
\begin{figure}[H]
\includegraphics[width=7cm]{algorithm_flowchart}
\centering
\caption{High-Level Image Processing Pipeline}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=7cm]{hsv_kmeans2_orig}
\includegraphics[width=7.5cm]{hsv_kmeans2_suppressed}
\centering
\caption{Boat Confidence Results}
\label{fig:boatconf}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{diff_magnitude}
\caption{Difference between the measured and modelled optical flow.
         Dark blue means perfect match, bright yellow means a poor match (and
         higher likelihood of an object).
         The sky is later filtered out by ignoring that half of the image.}
\label{fig:diff_magnitude}
\end{figure}

\begin{figure}
\hfill
\subfigure[Blobs pre-filtering]{\includegraphics[width=0.23\textwidth]{threshold_bwlabel}}
\hfill
\subfigure[Blobs
post-filtering]{\includegraphics[width=0.23\textwidth]{filtered_labels}}
\hfill
\caption{Results of blob detection on HSV and optical flow confidences}
\label{fig:blobs}
\end{figure}

@@

\begin{description}
\sloppy
\item  \footnote{\url{https://drive.google.com/file/d/1FoKWkp5xDSKwp5YyluKrclo_kGFU4gsg/view?usp=sharing}}
  In this video we have a longer view of the same boat as Figure
  \ref{fig:example_detection}
\item \footnote{\url{https://drive.google.com/file/d/1ndVSwF77_4va6U8rWT4FGJOXq1AjKL_Z/view?usp=sharing}}
  This has a slightly shorter capture of a different boat, indicating some
  degree of robustness to different individual instances
  \ref{fig:example_detection}
\end{description}

@@

\section{Robustness}

\begin{figure}[H]
\includegraphics[width=7cm]{sample1}
\centering
\caption{Mirror-like water}
\label{fig:mirror}
\end{figure}

While the algorithms do work reasonably well for footage from these particular
conditions, we had troubles processing some parts of the data. In particular,
early mornings when not only was the sun interfering with the camera,
but also in situations such as Figure \ref{fig:mirror}, in which the water is
relatively flat (reducing texture) and highly reflective, meaning that it is no
longer particularly blue. The algorithm also struggles when pointed in the
 direction of the sun, as the reflections off of the water tend to oversaturate the image sensor.
